---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MWMouseWeight

<!-- badges: start -->
<!-- badges: end -->

MWMouseWeight  is an R package designed to streamline the data cleaning, preparation, and initial analysis process for experimental datasets, which in this case particularly involves mice body weight and treatment outcomes. This package addresses common data inconsistencies, enables efficient wrangling, and provides key visualizations and summaries for further exploration.

Why Should I Use This Package?
MW offers several benefits, including automated cleaning to resolve typographical errors, correct non-numeric entries, and standardize labels. This package facilitates consistent wrangling, transforming datasets into analysis-ready formats with intuitive functions. Another insightful tool included is visualizations using plots, which allows users to quickly plot trends and summarize key statistics, saving time and reducing errors in the preprocessing stage.

## About the data

Data was made available by Professor James Xenakis in Harvard's Statistics 108 course. The MWMouseWeight package cleans the data and removes faulty mice, as detailed in the dataset.r file. Specifically, with the data wrangling portion of MWMouseweight, the following concerns are addressed: first, the inconsistencies of naming styles and data collection was solved (for example, inconsistent naming of treatment (‘Tmt’, Trmt) was standardized and made uniform across the mice. The issues were prevalent throughout the dataset, including in the names of columns. Next, ineligible mice (those who had died or experienced a body weight decrease of 20 percent or more) were removed from the dataset. Lastly, the scattered data was aggregated into one final dataset.  Ultimately, the MWMouseWeight contains four datasets. Ultimately, the MWMouseWeight contains four datasets. While more information can be found regarding the datasets in the documentation of the dataset, here is a quick summary the datasets and what they contain:

The first dataset is called 'birth_data', and it contains mostly identification information about the mice in the study.

The second dataset is 'bodyweight_data', which contains information on how the mice's bodyweight changed over the three checkpoints. It also contains the dates of each checkpoint.

The third dataset is called 'outcome_data'. Since MWMouseWeight primarily focuses on the body weight of the mice, this dataset is not the most relavent for the functionality of the dataset. 

The fourth dataset is 'merged_data', which is all of these three datasets joined on mouse ID.

The fifth and final dataset we utilised is called 'miceweights.' We thank Evagoras Georgiou for providing this dataset and the Kaggle platform for hosting it. Miceweights contains data related to the weights of mice, designed for statistical analysis and modeling purposes. Within this dataset includes feeding types, either standard chow to hf, high fat, diets.This dataset can be used to explore trends, relationships, and patterns in mouse weights. There is also no license on this particular datset making it accessible to the public.

## Installation

You can install the development version of MWMouseWeight like so:

``` r
install.packages("devtools")
devtools::install_github("yourusername/MWMouseWeight")

```

## Example

This is a basic example which shows you how to solve a common problem:

For visualization, you can use the `plot_mouse_weight()` function to visualize body weight trends over time. More detailed examples and extended analyses can be found in the package vignette.

```{r example}
library(MWMouseWeight)
## basic example code
plot_mouse_weight(merged_data)
```

